---
title: "Dialogue"
author: "J. Hagedorn"
output: 
  md_document:
    variant: markdown_github
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("search_go.R"); source("get_genes.R"); source("get_patterns.R"); source("get_words.R")
```

```{r}
dialogue_genes <-
  get_genes(
    go_ids = c(
      `cell communication` = "GO:0007154",
      `cell communication by chemical coupling` = "GO:0010643",
      `cell communication by electrical coupling` = "GO:0010644",
      `positive regulation of cell communication` = "GO:0010647",
      `SA node cell-atrial cardiac muscle cell adhesion involved in cell communication` = "GO:0086022",
      `Purkinje myocyte to ventricular cardiac muscle cell communication` = "GO:0086068"
    )
  )
```

GJD3: Gap junction delta-3 protein; One gap junction consists of a cluster of closely packed pairs of transmembrane channels, the connexons, through which materials of low MW diffuse from one cell to a neighboring cell.
 
ANG: Angiogenin is a key protein implicated in angiogenesis (physiological process through which new blood vessels form from pre-existing vessels) in normal and tumor growth

Print stanza patterns...

```{r get_patterns, message=FALSE, warning=FALSE, paged.print=FALSE}
skin_patterns <- get_patterns(gene_id = "GJD3")
poem_pattern <- skin_patterns$tercet_amino$pattern
```

`r head(poem_pattern)`

Select word similarity patterns...
```{r get_atcg}

a_words <- get_words(
  "regex",
  "^(^(?!un|dis|mis|over|non|up.*$).*)(ough$|to$|ew$|oo$|ue$).*$",
  pattern_alias = "through_rhyme",
  min_len = 3, max_len = 9, is_common = F
)
t_words <- get_words(
  "regex",
  # Words with same start and end letter
  "^([a-z]).*\\1$",
  pattern_alias = "circle",
  min_len = 5, max_len = 11, is_common = T #, stem = T
)
c_words <- get_words(
  "regex",
  "^(^(?!un|dis|mis|over|non|up.*$).*)(nst$|ends$|ens$|end$|en$).*$",
  pattern_alias = "against_rhyme",
  min_len = 3, max_len = 9, is_common = T
)
g_words <- get_words(
  "regex",
  # Words with only one kind of vowel 
  "(^((?![eiouy]).)*$|^((?![aiouy]).)*$|^((?![aeouy]).)*$|^((?![aeiuy]).)*$|^((?![aeioy]).)*$|^((?![aeiou]).)*$)",
  pattern_alias = "single_vowel",
  min_len = 5, max_len = 11, is_common = T #, stem = T
)

```

---

# Legend

*Below are the first 100 lines of the poem's pattern, labelled:*

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(magrittr)

legend <- 
  poem_pattern %>%
  str_sub(1,100) %>%
  str_replace_all(pattern = "|",replacement = "  \n") %>%
  str_replace_all(pattern = "a",replacement = " a") %>%
  str_replace_all(pattern = "t",replacement = " t") %>%
  str_replace_all(pattern = "c",replacement = " c") %>%
  str_replace_all(pattern = "g",replacement = " g") %>%
  str_replace_all(pattern = " a",replacement = a_words$word_pattern) %>%
  str_replace_all(pattern = " t",replacement = t_words$word_pattern) %>%
  str_replace_all(pattern = " c",replacement = c_words$word_pattern) %>%
  str_replace_all(pattern = " g",replacement = g_words$word_pattern) 
  
cat(legend)
```


---

# Word options

## A

The pattern is: `r a_words$word_pattern`

Words include:

`r a_words$words$word`

---

## T

The pattern is: `r t_words$word_pattern`

Words include:

`r t_words$words$word`

---

## C

The pattern is: `r c_words$word_pattern`

Words include:

`r c_words$words$word`

---

## G

The pattern is: `r g_words$word_pattern`

Words include:

`r g_words$words$word`
