---
title: "Speak, muse (DCANP1)"
author: "J. Hagedorn"
date: "October 14, 2018"
output: 
  pdf_document:
    toc: true
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("search_go.R"); source("get_genes.R"); source("get_patterns.R"); source("get_words.R")
```

The gene is involved in *"the process that gives rise to the vestibulocochlear nerve...this sensory nerve innervates the membranous labyrinth of the inner ear... that senses head position changes relative to gravity [and] is connected to the three bony ossicles which transduce sound waves into fluid movement"*

It is involved in the following:

- hearing [*auditory behavior, cochlea development, cochlea morphogenesis, inner ear development, inner ear morphogenesis, vestibulocochlear nerve formation*]
- speech [*learned vocalization behavior*]
- balance [*neuromuscular process controlling balance, negative regulation of relaxation of muscle, regulation of muscle organ development, thorax and anterior abdomen determination, vestibulocochlear nerve formation*]
- formation of the skull's echo chamber [*craniofacial suture morphogenesis, hard palate morphogenesis*]
- hunger, eating [*negative regulation of saliva secretion, peristalsis, mastication, trigeminal nerve development,negative regulation of relaxation of muscle*]
- hunger, sex [*genitalia development, genitalia morphogenesis*]

Print stanza patterns...

```{r get_patterns, message=FALSE, warning=FALSE, paged.print=FALSE}
hearing_patterns <- get_patterns(gene_id = "DCANP1")
poem_pattern <- hearing_patterns$couplet_amino$pattern
```

`r head(poem_pattern)`

Select word similarity patterns...
```{r get_atcg}
a_words <- get_words("category", "sound")
t_words <- get_words("regex","^[aeiou](\\w|\\s)*[aiou]$", min_len = 4, max_len = 6) 
c_words <- get_words("letter_proportion","vowel", prop = 0.5, min_len = 6, max_len = 10)
g_words <- get_words("vocal_proportion","plosives", prop = 0.33, min_len = 4, max_len = 9) 
```

---

# Legend

*Below are the first 100 lines of the poem's pattern, labelled:*

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(magrittr)

legend <- 
  poem_pattern %>%
  str_sub(1,100) %>%
  str_replace_all(pattern = "|",replacement = "  \n") %>%
  str_replace_all(pattern = "a",replacement = " a") %>%
  str_replace_all(pattern = "t",replacement = " t") %>%
  str_replace_all(pattern = "c",replacement = " c") %>%
  str_replace_all(pattern = "g",replacement = " g") %>%
  str_replace_all(pattern = " a",replacement = a_words$word_pattern) %>%
  str_replace_all(pattern = " t",replacement = t_words$word_pattern) %>%
  str_replace_all(pattern = " c",replacement = c_words$word_pattern) %>%
  str_replace_all(pattern = " g",replacement = g_words$word_pattern) 
  
cat(legend)
```


---

# Word options

## A

The pattern is: `r a_words$word_pattern`

Words include:

`r a_words$words$word`

---

## T

The pattern is: `r t_words$word_pattern`

Words include:

`r t_words$words$word`

---

## C

The pattern is: `r c_words$word_pattern`

Words include:

`r c_words$words$word`

---

## G

The pattern is: `r g_words$word_pattern`

Words include:

`r g_words$words$word`
