---
title: "Blood"
author: "J. Hagedorn"
output: 
  md_document:
    variant: gfm
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../funs/search_go.R"); source("../../funs/get_genes.R"); 
source("../../funs/get_patterns.R"); source("../../funs/get_words.R")
```

```{r}

search_go("blood") %>% View()

searches <- list()
searches$blood_genes <-
  get_genes(
    go_ids = c(
      #`blood circulation` = "GO:0008015",
      `regulation of systemic arterial blood pressure by atrial baroreceptor feedback` = "GO:0002015",
      `branching involved in blood vessel morphogenesis` = "GO:0001569",
      `blood vessel endothelial cell proliferation involved in sprouting angiogenesis` = "GO:0002043",
      `activation of blood coagulation via clotting cascade` = "GO:0002543",
      `circadian regulation of systemic arterial blood pressure` = "GO:0003052",
      `circadian regulation of systemic arterial blood pressure by the suprachiasmatic nucleus` = "GO:0003054",
      `feeding on blood of other organism` = "GO:0044369"
    )
  )

searches$blood_genes %>% View()
```

RNA-binding protein that acts as a key regulator of N6-methyladenosine (m6A) methylation of RNAs, thereby regulating different processes, such as hematopoietic cell homeostasis, alternative splicing of mRNAs and X chromosome inactivation mediated by Xist RNA (PubMed:27602518). Associated component of the WMM complex, a complex that mediates N6-methyladenosine (m6A) methylation of RNAs, a modification that plays a role in the efficiency of mRNA splicing and RNA processing (By similarity). Plays a key role in m6A methylation, possibly by binding target RNAs and recruiting the WMM complex (PubMed:27602518). Involved in random X inactivation mediated by Xist RNA: acts by binding Xist RNA and recruiting the WMM complex, which mediates m6A methylation, leading to target YTHDC1 reader on Xist RNA and promoting transcription repression activity of Xist (PubMed:27602518). Required for the development of multiple tissues, such as the maintenance of the homeostasis of long-term hematopoietic stem cells and for megakaryocyte (MK) and B-cell differentiation (By similarity). Regulates megakaryocyte differentiation by regulating alternative splicing of genes important for megakaryocyte differentiation; probably regulates alternative splicing via m6A regulation (PubMed:26575292). Required for placental vascular branching morphogenesis and embryonic development of the heart and spleen (By similarity). Acts as a regulator of thrombopoietin response in hematopoietic stem cells by regulating alternative splicing of MPL (By similarity). May also function as an mRNA export factor, stimulating export and expression of RTE-containing mRNAs which are present in many retrotransposons that require to be exported prior to splicing (PubMed:17001072, PubMed:19786495). High affinity binding of pre-mRNA to RBM15 may allow targeting of the mRNP to the export helicase DBP5 in a manner that is independent of splicing-mediated NXF1 deposition, resulting in export prior to splicing (PubMed:17001072, PubMed:19786495). May be implicated in HOX gene regulation (PubMed:11344311)

Haematopoiesis is the formation of blood cellular components. All cellular blood components are derived from haematopoietic stem cells.  In a healthy adult person, approximately 10¹¹–10¹² new blood cells are produced daily in order to maintain steady state levels in the peripheral circulation

Print stanza patterns...

```{r get_patterns, message=FALSE, warning=FALSE, paged.print=FALSE}
blood_patterns <- get_patterns(gene_id = "RBM15")
poem_pattern <- blood_patterns$couplet_pair$pattern

library(Biostrings)

codons <- 
  DNAString(
    blood_patterns$gene_df %>% 
    mutate(nucleotide = str_to_upper(nucleotide)) %>% 
    summarize(string = paste(nucleotide, collapse = "")) %>%
    .$string
  ) %>% 
  translate()

tst <- alphabetFrequency(codons[1:50])

tst[tst > 0]

```

`r head(poem_pattern)`

Select word similarity patterns...
```{r get_atcg}

a_words <- get_words(
  "letter_proportion", "vowel", 
  pattern_alias = "vowelicious",
  prop = 0.6, min_len = 4, max_len = 9 #, is_common = T
)
t_words <- get_words(
  "letter_proportion", "consonant", 
  pattern_alias = "consonants",
  prop = 0.8, min_len = 5, max_len = 9, is_common = T
)
c_words <- get_words(
  "vocal_proportion", "frictionless", 
  pattern_alias = "frictionless",
  prop = 0.25, min_len = 4, max_len = 9#, is_common = T
)
g_words <- get_words(
  "vocal_proportion", "fricatives", 
  pattern_alias = "fricative",
  prop = 0.4, min_len = 4, max_len = 9, #is_common = T
)

```

---

# Legend

*Below are the first 100 lines of the poem's pattern, labelled:*

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(magrittr)

legend <- 
  poem_pattern %>%
  str_sub(1,100) %>%
  str_replace_all(pattern = "|",replacement = "  \n") %>%
  str_replace_all(pattern = "a",replacement = " a") %>%
  str_replace_all(pattern = "t",replacement = " t") %>%
  str_replace_all(pattern = "c",replacement = " c") %>%
  str_replace_all(pattern = "g",replacement = " g") %>%
  str_replace_all(pattern = " a",replacement = a_words$word_pattern) %>%
  str_replace_all(pattern = " t",replacement = t_words$word_pattern) %>%
  str_replace_all(pattern = " c",replacement = c_words$word_pattern) %>%
  str_replace_all(pattern = " g",replacement = g_words$word_pattern) 
  
cat(legend)
```


---

# Word options

## A

The pattern is: `r a_words$word_pattern`

Words include:

`r a_words$words$word`

---

## T

The pattern is: `r t_words$word_pattern`

Words include:

`r t_words$words$word`

---

## C

The pattern is: `r c_words$word_pattern`

Words include:

`r c_words$words$word`

---

## G

The pattern is: `r g_words$word_pattern`

Words include:

`r g_words$words$word`
